Turnover of species and interactions

### 2019-05-08 paper/data-exploration/turnover.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.asp = 10/16)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, dpi = 300, fig.asp = 10/16, warning = FALSE)
```

@@

## Data completeness

```{r}
drake::loadd(n_occurrences)

n_occurrences %>%
  dplyr::group_by(sp_name, n, guild, n_occurrences) %>%
  dplyr::do(canon_name = unlist(.$backbone[[1]]$canonicalName)) %>% 
  dplyr::group_by() %>%
  dplyr::mutate(sp_name = forcats::fct_reorder(sp_name, n), 
                n_occurrences = dplyr::if_else(sp_name != canon_name, 
                                               NA_integer_, 
                                               as.integer(n_occurrences))) %>%
  humanize() %>%
  ggplot(aes(y = n_occurrences, x = sp_name, colour = guild)) +
  geom_point() +
  geom_segment(aes(xend = sp_name, yend = 0)) +
  scale_y_log10() +
  coord_flip() +
  scale_color_brewer(palette = "Paired") +
  theme_bw() +
  theme(axis.text.y = element_text(face = "italic", size = 6)) +
  labs(x = "", y = "# occurrences", 
       title = "GBIF occurrences", 
       subtitle = "number of GBIF georeferenced records per species", 
       caption = "species ordered by how likely they are to be included as focal species")
```

```{r, fig.asp=3}
drake::loadd(maps)

selected_sp_map <- n_occurrences %>%
  dplyr::slice(1:28) %>%
  extract2("sp_name")
maps %>% 
  dplyr::filter(layer != 0, 
                sp_name %in% selected_sp_map) %>%
  ggplot(aes(x,y)) +
  # mapWorld +
  geom_tile(aes(fill = layer)) +
  coord_quickmap() +
  theme_bw() +
  facet_wrap(~ sp_name, ncol = 2) +
  theme(legend.position = "none")
```
